R Notebook

### 2020-06-10 R/ICCHP20.Rmd
Finally ...

data.long <- data.wide %>%
  mutate(id = seq_along(Hotspot), .before = Hotspot) %>%
  pivot_longer(cols = "P1":"P4", names_to="Participant", names_transform = list(Participant = as.factor), values_to = "Time") %>%
  relocate(Participant, id, Condition, Hotspot, Time) %>%
  #mutate(Hotspot = factor(Hotspot, levels = hs.order, ordered = TRUE)) %>%
  dplyr::arrange(Participant, id) %T>% print
```
***
# Wilcoxon
***

@@

```{r}
hist1 <-
  data.long %>% gghistogram(
    x = "Time",
    rug = T,
    add = "median",
    color = "Condition",
    fill = "Condition",
    alpha=0.75,
    palette = c("#00AFBB", "#f48806"),
    bins = 20,
    xticks.by=20,
    xlab = "Time to find hotspot",
    ylab = "Count"
  )

hist2 <-
  data.long %>% gghistogram(
    x = "Time",
    rug = T,
    add = "median",
    color = "Condition",
    fill = "Condition",
    alpha=0.75,
    palette = c("#00AFBB", "#f48806"),
    bins = 20,
    xticks.by=20,
    xlab = "Time to find hotspot",
    ylab = "Count",
    facet.by = "Condition"
  )

hist1
ggsave("../res/img/hist1.png", hist1, device = "png", dpi=320)
hist2
ggsave("../res/img/hist2.png", hist2, device = "png", dpi=320)
```

@@

```{r warnings=T}
test <- data.long %>% 
  select(Hotspot, Participant, Condition, Time) %>%
  group_by(Condition) %>% 
  mutate(Hotspot = factor(Hotspot, levels=hs.order)) %>% 
  ungroup %>%
  arrange(Participant, Hotspot) %T>% print

#data.long$Hotspot <- factor(data.long$Hotspot, levels = hs.order)

fig.full <- ggdotchart(
  test,
  x = "Hotspot",
  y = "Time",
  color = "Condition",
  #shape = "Condition",
  palette = c("#00AFBB", "#f48806"),
  add = "segments",
  add.params = list(color = "lightgray", size = 1.5),
  group = "Condition",
  dot.size = 4,
  #label = "Time",
  font.label = list(
    color = "white",
    size = 8,
    vjust = 0.5
  ),
  facet.by = "Participant",
  xlab = "Hotspot",
  ylab = "Time to find hotspot",
  ylim = c(0, 130),
  yticks.by = 20
)

>>>>

data.long <- data.wide %>%
  mutate(id = seq_along(Hotspot), .before = Hotspot) %>%
  pivot_longer(cols = "P1":"P4", names_to="Participant", names_transform = list(Participant = as.factor), values_to = "Time") %>%
  relocate(Participant, id, Condition, Hotspot, Time) %>%
  #mutate(Hotspot = factor(Hotspot, levels = hs.order)) %>%
  dplyr::arrange(Participant, id) %T>% print
```
***
# Wilcoxon
***

@@

```{r}
data.long %>% gghistogram(
  x = "Time",
  rug = T,
  add = "median",
  color = "Condition",
  fill = "Condition",
  alpha = 0.75,
  palette = c("#00AFBB", "#f48806"),
  bins = 20,
  xticks.by = 20,
  xlab = "Time to find hotspot",
  ylab = "Count",
  facet.by = "Condition"
)

ggsave("../res/img/hist.png", device = "png", dpi = 320)
```

@@

```{r warnings=T}
fig.full <- ggdotchart(
  data.long,
  x = "Hotspot",
  y = "Time",
  color = "Condition",
  #shape = "Condition",
  palette = c("#00AFBB", "#f48806"),
  add = "segments",
  add.params = list(color = "lightgray", size = 1.5),
  group = "Hotspot",
  dot.size = 4,
  #label = "Time",
  font.label = list(
    color = "white",
    size = 8,
    vjust = 0.5
  ),
  facet.by = "Participant",
  xlab = "Hotspot",
  ylab = "Time to find hotspot",
  ylim = c(0, 130),
  yticks.by = 20
) #+ scale_x_discrete(labels=hs.order)
